Chapter 3 Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks

### 2015-12-08 manuscript/manuscript_wtc3.Rmd
tried to add chapters to title:fail
hid corresponding author

---
title: "Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---

@@

\
*Corresponding author*: 
Courtney Campany
E: courtneycampany@gmail.com

>>>>

---
title: "Chapter 3 Rapid response of mesophyll conductance to light availability allows shade leaves to take advantage of sunflecks"
author: ""
date: ""
output:
  word_document:
    reference_docx: manuscriptstyle_thesis.docx
  pdf_document: default
  html_document:
    number_sections: yes
csl: new-phytologist.csl
bibliography: references.bib
---

@@

<!-- \ -->
<!-- *Corresponding author*: -->
<!-- Courtney Campany -->
<!-- E: courtneycampany@gmail.com -->
